Exploratory Analysis Ethan Schilling

### 2025-12-09 Exploratory Analysis Ethan SchillingREAL.Rmd
WORKRKKKKRKR
added some more models with RMSE and MAE

# 1 Interaction Term
model1 <- lm(FeCl_dose ~ mean_Temp * mean_Turbidity + mean_pH + Temp_lag1 + Turb_lag1, 
             data = train)
summary(model1)

@@

rmse(test$FeCl_dose, test$pred_model1)
mae(test$FeCl_dose, test$pred_model1)

# 2 Interaction Terms
model2 <- lm(FeCl_dose ~ mean_Temp * mean_pH +mean_Conductivity * mean_Turbidity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2, data = train)

@@

rmse(test$FeCl_dose, test$pred_model2)
mae(test$FeCl_dose, test$pred_model2)

# Step Up

response_var <- "FeCl_dose" 
predictors <- c("mean_Temp", "mean_pH", "mean_Conductivity",
                "mean_Turbidity", "Temp_lag1", "Temp_lag2",
                "pH_lag1", "pH_lag2", "Cond_lag1", "Cond_lag2",
                "Turb_lag1", "Turb_lag2")

>>>>

# 1 Interaction Term

model1 <- lm(FeCl_dose ~ mean_Temp * mean_pH + mean_Turbidity + Temp_lag1 + Turb_lag1, 
             data = train)
summary(model1)

@@

cat("Model 1 RMSE:", rmse(test$FeCl_dose, test$pred_model1), "\n")
cat("Model 1 MAE :", mae(test$FeCl_dose, test$pred_model1), "\n")

# 2 Interaction Terms

model2 <- lm(FeCl_dose ~ mean_Temp * mean_pH + mean_Conductivity * mean_Turbidity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2, data = train)

@@

cat("Model 2 RMSE:", rmse(test$FeCl_dose, test$pred_model2), "\n")
cat("Model 2 MAE :", mae(test$FeCl_dose, test$pred_model2), "\n")

model3 <- lm(FeCl_dose ~ mean_Temp * mean_Conductivity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2, data = train)

test$pred_model3 <- predict(model3, newdata = test)

cat("Model 3 RMSE:", rmse(test$FeCl_dose, test$pred_model3), "\n")
cat("Model 3 MAE :", mae(test$FeCl_dose, test$pred_model3), "\n")

# 2 Interactions: Cond and PH and Temp and Cond

model4 <- lm(FeCl_dose ~ mean_Conductivity * mean_pH + mean_Temp * mean_Conductivity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2, data = train)

test$pred_model4 <- predict(model4, newdata = test)

cat("Model 4 RMSE:", rmse(test$FeCl_dose, test$pred_model4), "\n")
cat("Model 4 MAE :", mae(test$FeCl_dose, test$pred_model4), "\n")
